Machine Learning Models for the Segmentation of eCoaching Text

### 2018-03-05 paper-amia-2018/manuscript.tex
update discussion

\begin{table}[ht]
\centering
\caption{Weighted average performance of NB, SVM, KNN, and RNN for the segmentation of eCoaching text in detecting both ``boundary'' and ``not boundary''. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only)}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topics except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score}\\ \hline

@@

\section*{Discussion}
This study is the first large-scale efforts to evaluate the segmentation of eCoaching text. Experimental results indicate that KNN achieved the best results among all machine learning methods considered for this study. KNN achieved 0.986 F1-score in overall, 0.779 and 0.993 F1-scores for detecting ``boundary'' and ``not boundary'', respectively. Robust performance of KNN provides the evidence that machine learning models are capable to learn information from the email exchange. Although the domain of this study was intentinally quite small, we believe that our study is not limited to ecoacing domain, and it can be successfully applied to other domain as well.

>>>>

\begin{table}[ht]
\centering
\caption{Weighted average performance of NB, SVM, KNN, and RNN for the segmentation of eCoaching text in detecting both ``boundary'' and ``not boundary''. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{contextual features only}} & \multicolumn{3}{|c|}{\textbf{contextual + punctuation marks (+ topics except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score}\\ \hline

@@

\section*{Discussion}
This study is the first large-scale efforts to evaluate the segmentation of eCoaching text. Experimental results indicate that KNN is the best model among all machine learning methods considered for this study. KNN achieved 0.986 F1-score in overall, 0.779 and 0.993 F1-scores for detecting ``boundary'' and ``not boundary'', respectively. Robust performance of KNN provides the evidence that machine learning models are capable to learn information from the email exchange. Although the domain of this study was intentinally quite small, we believe that our study is not limited to ecoacing domain, and it can be successfully applied to other domain as well.
